\phantomchapter{Acknowledgements}
I would like to express my sincere gratitude to the following people for their assistance, guidance, and support during this study:

\begin{itemize}
    \item My supervisor, Prof. P, Y. Tabakov for his continual guidance, advice, and mentorship throughout my research. His patience with my endless queries, extensive knowledge of engineering studies, and enthusiasm for the whole project were great motivations, and I am very thankful to him.

    \item My former colleague, Mapule Molabe for her continual assistance from the commencement of this report. You know this thesis would have not even started without your technical expertise, and for that I thank you.  

    \item My friend, Andile Ntanjana for his continual assistance in reviewing my report regularly and providing technical expertise was necessary.

    \item My friend, Yamkelani Mlunguza for her continual assistance in reviewing my report and guiding me in the right direction throughout the years. 

    \item I would also like to extend my sincere gratitude to my family members and my dearest friends for their unwavering support throughout my degree study.
    
    \item Special gratitude goes to National Research Foundation (NRF) for their funding (reference \textbf{MND200611530513}). It also brings me great pleasure to convey my appreciation to Columbus Stainless (Pty) Ltd for supplying the duplex stainless steel for experimental purposes. Lastly, the Durban University of Technology (DUT) for assisting with \acrshort{ftir} and \acrshort{dls} instruments.
 \end{itemize}