\phantomchapter{Declaration}
I, \textbf{Nhlanhla Fortune Khanyi}, declare that:   

\begin{enumerate}
    \item The research reported in this thesis, except where otherwise indicated, is my original research. 
    \item The thesis has not been submitted for any degree or examination at any other university. 
    \item This thesis does not contain other persons' data, pictures, graphs, or other information unless specially acknowledged as being sourced from other persons.  
    \item This thesis does not contain other persons' writing unless specially acknowledged as being sourced from other researchers. Where other written sources have been quoted, then:  
    
    \begin{enumerate}
        \item Their words have been rewritten, but the general information attributed to them has been referenced.  
        \item Where their exact words have been used, then their writing has been placed in italics and inside quotation marks and referenced.  
    \end{enumerate} 
    
    \item This thesis does not contain text, graphics, or tables copied and pasted from the internet unless specially acknowledged, and the source is detailed in the thesis and the reference sections. 
\end{enumerate}

\begin{flushright}
April, 2023.
\end{flushright} 

\vspace{1cm}

\newcommand{\writingspace} {\rule{5cm}{0.2mm}}
{\renewcommand{\arraystretch}{1.6}

\begin{tabularx}{\textwidth}{ >{\hsize=1.3\hsize}X >{\hsize=0.5\hsize}X }
Student: \writingspace & \writingspace\\
N.F. Khanyi	& Date \\
\\
Supervisor: \writingspace & \writingspace\\
Prof. P,Y. Tabakov & Date 
\end{tabularx}}